# What is NOC Internationalization? {#paper1}

## Introduction {#intro01}

<!-- Word Count, August 28th: 7,545 -->

```{r prelims, warning=F, message=F, echo=F}
library(tidyverse)
library(ggthemes)
library(knitr)

load("data/out/etl_results.RData")
```

```{r, include=F}
options(knitr.table.format = "latex")
```

In December of 2014, the Russian government engaged a drastic interest rate hike in the hopes of defending the ruble. There are a number of reasons for the Russian currency's precipitous decline in recent months --- these include the stock market cost of military adventurism in Ukraine and the general decline in oil prices. The drop in the ruble's value in mid-December, however, has been linked by observers to an "opaque deal involving the central bank and the state-controlled oil company, Rosneft"" [@kramer_russias_2014]. The oil company, *The New York Times* goes on to report, "had been clamoring for months for a government bailout to refinance debt the company ran up while making acquisitions when oil prices were high."























